Object Naming in Language and Vision: A Survey and a New Dataset

### 2020-03-12 papers/LREC2020/survey.tex
shortens Gemma's new intro

However, there is a crucial pitfall: As Figure~\ref{fig:bird} shows, there is only a partial linking of objects that are mentioned across different region descriptions; for instance, the first, second, and fifth object IDs in the figure actually correspond to the same object.
Moreover, the regions for the beak of the object (third and fourth object IDs) overlap with those of the bird. 
%This means that the identity of objects cannot be established based on the annotation, which severely limits the usefulness of the data to analyze naming.
%For instance, even though there is a different name (\word{vulture}) for \word{bird} in Figure~\ref{fig:bird}, the annotation suggests that \word{bird} is the only available name. 
Finally, even though there is a different name (\word{vulture}) for \word{bird} in Figure~\ref{fig:bird}, the annotation suggests that \word{bird} is the only available name. 
Hence, the identity of objects cannot be established based on the annotation, which severely limits the usefulness of the data to analyze naming.
The relatively low number of $1.7$~annotations per objects on average in VG (Table~\ref{tab:compare}) and the very small number of objects that have more than one name associated with it ($2$\%) seem to be an effect of this partial linking problem.
We experimented with filtering and merging bounding boxes based on overlap, but this would introduce substantial noise into the data (e.g.,~truly overlapping objects).

@@

\begin{figure}
\begin{center}
%\fbox{\parbox{6cm}{
%This is a figure with a caption.}}
\includegraphics[scale=0.32]{figures/vulture.png} 
\begin{tabular}{lp{6cm}}
object id & linked region descriptions\\
\hline
3595788 & the \textbf{bird} is black in color, nose of the \textbf{bird}, a \textbf{bird} relaxing in stand, small white beak of \textbf{bird}, large black talon of \textbf{bird}, a \textbf{bird} on a green pole, a green bar under \textbf{bird}, black \textbf{bird} on green rail, small black eye of \textbf{bird}\\
2286017 & large black \textbf{vulture} on fence, a vulture on bar\\
%2385747 & small white beak of \textbf{bird}\\
2681429 & a semi \textbf{long beak}\\  
2346210 & a black and gray \textbf{vulture}\\
 \end{tabular}
\caption{Bounding boxes, names and region descriptions for an object in VisualGenome}
\label{fig:bird}
\end{center}
\end{figure}

>>>>

However, there is a crucial pitfall: As Figure~\ref{fig:bird} shows, there is only a partial linking of objects that are mentioned across different region descriptions; for instance, the first, second, and fourth object ID in the figure actually correspond to the same object.
Moreover, the region for the beak of the object (third object IDs) overlaps with those of the bird. 
%This means that the identity of objects cannot be established based on the annotation, which severely limits the usefulness of the data to analyze naming.
%For instance, even though there is a different name (\word{vulture}) for \word{bird} in Figure~\ref{fig:bird}, the annotation suggests that \word{bird} is the only available name. 
Finally, even though there is a different name (\word{vulture}) for \word{bird} in Figure~\ref{fig:bird}, the annotation suggests that \word{bird} is the only available name. 
Hence, the identity of objects cannot be established based on the annotation, which severely limits the usefulness of the data to analyze naming.
The relatively low number of $1.7$~annotations per objects on average in VG (Table~\ref{tab:compare}) and the very small number of objects that have more than one name associated with it ($2$\%) seem to be an effect of this partial linking problem.
We experimented with filtering and merging bounding boxes based on overlap, but this would introduce substantial noise into the data (e.g.,~truly overlapping objects).

@@

\begin{figure}
\begin{center}
%\fbox{\parbox{6cm}{
%This is a figure with a caption.}}
\includegraphics[scale=0.25]{figures/vulture.png} 
\begin{tabular}{lp{6cm}}
object id & linked region descriptions\\
\hline
3595788 & the \textbf{bird} is black in color, nose of the \textbf{bird}, a \textbf{bird} relaxing in stand, small white beak of \textbf{bird}, large black talon of \textbf{bird}, a \textbf{bird} on a green pole, a green bar under \textbf{bird}, black \textbf{bird} on green rail, small black eye of \textbf{bird}\\
2286017 & large black \textbf{vulture} on fence, a vulture on bar\\
%2385747 & small white beak of \textbf{bird}\\
2681429 & a semi \textbf{long beak}\\  
2346210 & a black and gray \textbf{vulture}\\
 \end{tabular}
\caption{Bounding boxes, names and region descriptions for an object in VisualGenome}
\label{fig:bird}
\end{center}
\end{figure}
